Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-02-03 paper.qmd
Added linked plot section to Methods
Updated the data

true_model_df <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_true_model.rds")
wireframe_true_model <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_true_model_connections.rds")

data_two_curvy <- training_data_two_curvy |>
  mutate(type = "data")

@@

## First projection
projection <- cbind(
    c(0.11062,-0.02743,0.02786,-0.01930,0.02374,-0.03493,0.03159),
    c(-0.01110,-0.06886,0.04730,0.09890,-0.00571,-0.00038,0.00169))

@@

## Second projection
projection <- cbind(
    c(-0.03372,0.07726,0.03948,-0.00096,-0.02976,-0.07968,0.03194),
    c(0.07080,0.00316,-0.00382,0.05069,-0.07334,-0.02506,-0.05749))

@@

@@

## First projection
projection <- cbind(
  c(-0.08707,-0.06493,0.07017,-0.07349,-0.02955,-0.05286,-0.02765),
  c(0.03398,0.03735,0.09272,0.01871,-0.09224,0.00451,0.08079))

@@

## Linked plots

>>>>

true_model_df <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_true_model.rds")
wireframe_true_model <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_true_model_connections.rds")
training_data_two_curvy_not_std <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_data_without_std.rds")

data_two_curvy <- training_data_two_curvy_not_std |>
  mutate(type = "data")

@@

## First projection
projection <- cbind(
    c(0.11062,-0.02743,0.02786,-0.01930),
    c(-0.01110,-0.06886,0.04730,0.09890))

@@

## Second projection
projection <- cbind(
    c(-0.03372,0.07726,0.03948,-0.00096),
    c(0.07080,0.00316,-0.00382,0.05069))

@@

### Linked plots

@@

## First projection
projection <- cbind(
  c(-0.08707,-0.06493,0.07017,-0.07349),
  c(0.03398,0.03735,0.09272,0.01871))

@@
